Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex

product & measurement indices & price range (approx. USD) \\
\hline
FitBit & general activity (walking/jogging) & \$50 \\
Nike FuelBand & general activity (walking/jogging) & \$199 \\ 
Writhings WiFi Scale & weight & \$200 \\
Writhings BPM & blood pressure & \$200 \\ 
Zeo Pro & sleep duration \& quality & \$200 \\
WakeMate & sleep duration & \$50  \\
Zensorium Tinkne & heart rate variability, blood oxygenation, respiratory rate & \$200 \\
BodyMedia CORE 2 & galvanic skin repsonse, body temperature, sleep, respiratory rate, heart rate & (TBD) \\
Hapifork & eating time, rate, frequency & (TBD) \\ 
\end{tabular}
\caption{\emph{Consumer-grade activity sensors}: Activity and physiological measurement sensors with automatic data uplink to cloud services }
\label{sensors}
\end{table}
}
\vspace{6cm}

@@

The recent proliferation in personal wearable activity sensors and
network and storage- enabled digital health measurement devices has
been driven by both the falling costs of embeddable electronics, and a
surging public interest in ``quantified-self''-style self-monitoring
for self-improvement.  Many of these sensors are lightweight, can be
worn discreetly, measure several physiological statistics
simultaneously, and most require little maintenance. Table
\ref{sensors} lists a sampling of the sensors currently available
directly from retailers.

@@

However, many of these sites have APIs that provide programmatic access to raw sensor data.  Our approach has been touse such APIs to retrieve a patient's information from all services corresponding to their devices.  In particular, we propose that consolidating such information into a uniform, common taxonomy and description logic, like those provided by SNOMED-CT \cite{stearns2001snomed} and ICD-10 \cite{world1993icd} for diseases, would enable such diaries to be interpretable and used directly by future clinical medical systems, such as primary care information management systems.

>>>>

product & measurement indices & price range (approx. USD) \\
\hline
FitBit & general activity (walking/jogging) & \$50 \\
Nike FuelBand & general activity (walking/jogging) & \$199 \\ 
WiThings WiFi Scale & weight & \$200 \\
WiThings BPM & blood pressure & \$200 \\ 
Zeo Pro & sleep duration \& quality & \$200 \\
WakeMate & sleep duration & \$50  \\
Zensorium Tinnke & heart rate variability, blood oxygenation, respiratory rate & \$200 \\
BodyMedia CORE 2 & galvanic skin response, body temperature, sleep, respiratory rate, heart rate & (TBD) \\
Hapifork & eating time, rate, frequency & (TBD) \\ 
\end{tabular}
\caption{\emph{Consumer-grade activity sensors}: Activity and physiological measurement sensors with automatic data uplink to cloud services }
\label{sensors}
\end{table}
}
\vspace{6cm}

@@

The recent proliferation in personal wearable activity sensors and
network- and storage- enabled digital health measurement devices has
been driven by both the falling costs of embeddable electronics, and a
surging public interest in ``quantified-self''-style self-monitoring
for self-improvement.  Many of these sensors are lightweight, can be
worn discreetly, measure several physiological statistics
simultaneously, and most require little maintenance. Table
\ref{sensors} lists a sampling of the sensors currently available
directly from retailers.

@@

However, many of these sites have APIs that provide programmatic access to raw sensor data.  Our approach has been touse such APIs to retrieve a patient's information from all services corresponding to their devices.  In particular, we propose that consolidating such information into a uniform, common taxonomy and description logic, like those provided by SNOMED-CT~\cite{stearns2001snomed} and ICD-10~\cite{world1993icd} for diseases, would enable such diaries to be interpretable and used directly by future clinical medical systems, such as primary care information management systems.
